\documentclass[]{deedy-resume-openfont}
\begin{document}
\lastupdated

\namesection{Ricardo}{Avila}{
\href{https://ravila4.github.io}{\faExternalLink \space ravila4.github.io} \\
{\faEnvelopeO \space ravila11@miners.utep.edu} | \faPhone \space 915.781.0945
}

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{U. of Texas at El Paso}
\descript{MS in Bioinformatics}
\location{May 2019 | El Paso, TX}
\sectionsep

\descript{BS in Biochemistry}
\location{May 2016 | El Paso, TX}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ravila4}{\bf ravila4}\\
Linkedin:// \href{https://www.linkedin.com/in/ravila4/}{\bf ravila4}\\
Twitter://  \href{https://twitter.com/ravila_4}{\bf @ravila\_4}\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Comp. Modeling of Biostructures\\
Statistical Analysis \\
Statistical Programming \\
Bioinformatics I \& II \\
Postgenomic Analysis\\
Data Mining \\
Machine Learning \\
Database Management\\
Systems Neuroscience\\
\sectionsep

\subsection{Undergraduate}
Biochemistry I \& II \\
Structural Biochemistry\\
Molecular Cell Biology \\
%Prokaryotic Molecular Biology \\
Organic Chemistry I \& II \\
Physical Chemistry II \\
% Molecular Symmetry \& Group Theory \\
Discrete Mathematics \\
Data Structures and Algorithms\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Laboratory}
 \textbullet{} protein expression
 \textbullet{} SDS-PAGE\\
 \textbullet{} UV-Vis
 \textbullet{} crystal screening
 \textbullet{} HPLC\\
% \textbullet{} PCR
% \textbullet{} plasmid purification
% \textbullet{} NMR \\
\sectionsep

\subsection{Programming}
 \textbullet{} Python
 \textbullet{} UNIX Shell
 \textbullet{} Java
 \textbullet{} R \\
 \textbullet{} MySQL
\sectionsep

\subsection{Software \& Toolkits}
 \textbullet{} Git
 \textbullet{} Pyspark
 \textbullet{} Chimera
 \textbullet{} PyMol\\
 \textbullet{} RDKit
 %\textbullet{} AutoDock
 %\textbullet{} OpenBabel
 %\textbullet{} Rosetta
 \textbullet{} EMAN2
 \textbullet{} Relion\\
 %\textbullet{} VMD
 \textbullet{} Schrödinger tools
 %\textbullet{} CCG MOE
 \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}
\location{Native fluency:}
 \textbullet{}   English \textbullet{} Spanish \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Objective
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{About Me}
%Biochemist with knowledge of structural biochemistry, bioinformatics, and a mixture of wet/dry lab experience. Interested in drug discovery research and protein design.

Bioinformatics programmer with a background in structural biochemistry. Passionate about
computational modeling, and interested in applying data mining and machine learning tools to problems in protein structure determination, drug discovery, and the intersection of these areas with other -omics fields.

%applying data mining and machine learning algorithms to problems in structural bioinformatics, drug discovery, and high dimensional -omics data analysis.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Work Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{GlaxoSmithKline, via Atrium}
\descript{| Protein Design and Informatics Intern}
\location{May 2018 – August 2018 | Upper Providence, PA}
\sectionsep
\begin{tightemize}
\item Evaluated methods for identifying cryptic binding pockets in proteins.\item Wrote scripts to automate analysis of molecular dynamics (MD) data. \item Ran scalability benchmarks to optimize MD simulation performance.  \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Structure-Based Drug Discovery Lab}
\descript{| Graduate RA}
\location{May 2016 – Present | UTEP School of Pharmacy | El Paso, TX}
\begin{tightemize}
\item Development and testing of novel machine-learning scoring functions for the prediction of drug-target binding affinities, logP, and other properties. \item Generation of large datasets by data mining web resources and literature. \item Developed a pipeline for in silico drug discovery targeting GPCRs.% \item Contributed to open source projects.
\end{tightemize}
\sectionsep

%\runsubsection{Structure-Based Drug Discovery}
%\descript{| Self-Guided Graduate Researcher}
%\location{May 2016 – December 2017 | UTEP Bioinformatics Program | El Paso, TX}
%\begin{tightemize}
%\item  Worked on putting together a workflow for virtual screening %drugs to GPCR targets.\item Learned to use several tools for %molecular docking and virtual screening, including AutoDock and %Schrodinger's drug discovery suite. \end{tightemize}
%\sectionsep

\runsubsection{Structural Biochemistry Lab}
\descript{| Undergraduate RA}
\location{March 2014 – August 2015 | UTEP Chemistry Department | El Paso, TX}
\begin{tightemize}
\item Transformation of recombinant plasmids in BL21 cells. \item Bacterial expression and purification of proteins.\item Functional assays to evaluate protein folding activity. \item Cryo-EM image processing software for 3D structure determination.\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Workshops
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Workshops}
\runsubsection{MMTF Workshop \& Hackathon}\\
\location{May 7 - 9 2018 | San Diego Supercomputer Center, UCSD | San Diego, CA}
\begin{tightemize}
\item Learned about the Protein Data Bank's MMTF data format and its applications in structural data mining.
\item Used nglview, a structure visualization tool alongside Jupyter notebooks.
\item Learned to use Apache Spark with Python for big data analysis. \item Hackathon project:  script to characterize close contacts in the PDB. \end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Posters \& Presentations} 
\begin{tabular}{rll}
March 2018      & OpenEye CUP XVIII | Santa Fe, NM \\
                & Automated workflow for reproducible analysis of protein-ligand \\
                & scoring functions.\\
March 2017      & 12th Annual NMBIST Symposium on Microbiomics | Santa Fe, NM \\
                & In silico evaluation of human OX2 orexin receptor (hOX2R) \\
                & inhibitors using AutoDock and Glide. \\
%November 2016   & 19th UTEP/NMSU Workshop on Mathematics, Computer Science, \\
%                & and Computational Sciences | El Paso, TX \\
%                & Comparison of AutoDock and Glide in docking Suvorexant to the \\
%                & crystal structure of human OX2 receptor (hOX2R). \\
October 2015    & UTEP COURI Symposium | El Paso, TX \\
                & A point mutation in the Phi-EL chaperonin alters ring separation \\
                & and protein folding activity. \\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}